### 2016-09-29 conclusion_and_future_work.tex
Rearrange conclusion to match the current order of the paper

SymPy is a robust computer algebra system that provides a wide spectrum of
features both in traditional computer algebra and in a plethora of scientific
disciplines. This allows SymPy to be used in a first-class way with other
Python projects, including the scientific Python stack. Unlike many other CAS's, SymPy
is designed to be used in an extensible way: both as an end-user
application and as a library.

SymPy expressions are immutable trees of Python objects. SymPy uses Python both
as the internal language and the user language. This permits users to access to
the same
methods that the library implements in order to extend it for their needs.
Additionally, SymPy has a powerful assumptions
system for declaring and deducing mathematical properties of expressions.

SymPy supports a wide array of mathematical facilities. This includes
functions for assuming and deducing common mathematical facts,
simplifying expressions, performing common calculus operations, polynomial
manipulations, pretty printing
expressions, solving equations, and representing symbolic matrices. Other supported
facilities
include discrete math, concrete math, plotting, geometry, statistics,
polynomials, sets, series, vectors, combinatorics, group theory, code
generation, tensors, Lie algebras, cryptography, and special functions.
Additionally, SymPy contains submodules targeting certain specific physics domains,
such as classical mechanics and quantum mechanics.  This breadth of domains has
been engendered by a strong and vibrant user community.
Anecdotally, these users likely chose SymPy because of its ease of access.

>>>>

SymPy is a robust computer algebra system that provides a wide spectrum of
features both in traditional computer algebra and in a plethora of scientific
disciplines. This allows SymPy to be used in a first-class way with other
Python projects, including the scientific Python stack.

SymPy supports a wide array of mathematical facilities. This includes
functions for assuming and deducing common mathematical facts,
simplifying expressions, performing common calculus operations, manipulating polynomials, pretty printing
expressions, solving equations, and representing symbolic matrices. Other supported
facilities
include discrete math, concrete math, plotting, geometry, statistics,
sets, series, vectors, combinatorics, group theory, code
generation, tensors, Lie algebras, cryptography, and special functions.
SymPy has strong support for arbitrary precision numerics, backed by the
mpmath package. Additionally, SymPy contains submodules targeting certain specific physics domains,
such as classical mechanics and quantum mechanics.  This breadth of domains has
been engendered by a strong and vibrant user community.
Anecdotally, many of these users chose SymPy because of its ease of access.
SymPy a dependency of many external projects across a wide
spectrum of domains.

SymPy expressions are immutable trees of Python objects. Unlike many other
CAS's, SymPy is designed to be used in an extensible way: both as an end-user
application and as a library. SymPy uses Python both as the internal language
and the user language. This permits users to access to the same methods used
by the library itself in order to extend it for their needs.
